Enter our title here

### 2017-08-08 manuscript.tex
started draft of intro

>>>>

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to unfold, the use of statistical software has become increasingly emphasized in statistics education. By integrating the capabilities of technology in introductory statistics courses, students can explore statistical ideas by analyzing and interpreting real data sets (Chance2007), giving them an authentic view of how statistics is practiced outside of the classroom (Broaddus2013). The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education} (GAISE) College Report has also prompted the use of more technology in introductory courses.

The goal for any introductory statistics course is to help students develope the ability to think statistically (AmericanStatisticalAssociation2016). 
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as variability, randomness and simulation.

Although numerous statistical technologies exist, \textit{R} and \textit{R Studio} provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses (Chance2007). R allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark an interest in the domain of statistics.

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R.

For a statistical learning tool to be effective, the software system should be modular, extensible, reproducable, and web-based (Hare2017).

Modulariy is critical component in designing a statistical learning tool; it allows independent pieces to be easily added, modified or removed from the entire functionality (Hare2017).
